Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
\newcommand{\system}{\textsc{CoCoSea}~}
\newcommand{\systemEnding}{\textsc{CoCoSea}}
\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{"#1"}}}}

@@

\section{Learning abstract geometry}
The brifly presented geometry project is a recent addition to the set of
problems adressed with our method.

The original DSL, while inspired by the Logo language~(\cite{abelson1974logo}) in the sense
that ones controls a moving on-off point, was designed to be congitively
plausible in the sense that some abstractions are baked in for curves and a few
structures --- it was first described in~\cite{sablemeyer2017geom}.

It is to be thought as a turtle with as internal state a position, a facing
direction, a speed, an acceleration, an angular speed and an angular
acceleration.

@@

In this context programs to be learned correspond to a single shape since they
don't take an input. All tasks will ignore input and produces a single output.
This differs from the previous examples where each target could be evaluated on
various input.

>>>>

\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\sem}[1]{\llbracket #1 \rrbracket}
\newcommand{\system}{\textsc{SCC}~}
\newcommand{\systemEnding}{\textsc{SCC}}
\newcommand{\lowerBound}{\mathscr{L}}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\newcommand{\codechar}[1]{{\footnotesize{\texttt{"#1"}}}}

@@

\section{Learning Generative Graphics Programs}

A natural extension of our work is to consider the problem of learning generative models:
here, we would learn programs that generate (either deterministically or probabilistically)
structures like images or words.
As a first step in this direction,
we apply \system to synthesizing graphics programs.

A natural starting DSL for graphics programming is the
Logo language~(\cite{abelson1974logo}), also sometimes called \textbf{turtle graphics}.
These programs control a pen (sometimes called a ``turtle''),
and can do things like pick the pen up,
move the pen forward,
rotate the pen,
or trace out a programmatically specified arc.
We take turtle graphics primitives from prior work~\cite{sablemeyer2017geom}.
In our setting, we will encapsulate turtle graphics primitives inside of $\lambda$-calculus,
and seek to infer graphics programs from images: thus the task is to look at an image,
and write the program that would have drawn it.

%% The brifly presented geometry project is a recent addition to the set
%% of problems adressed with our method.

%% The original DSL, while inspired by the in the sense that ones
%% controls a moving on-off point, was designed to be congitively
%% plausible in the sense that some abstractions are baked in for curves
%% and a few structures ---

%% It is to be thought as a turtle with as internal state a position, a
%% facing direction, a speed, an acceleration, an angular speed and an
%% angular acceleration.

@@

%% In this context programs to be learned correspond to a single shape since they
%% don't take an input. All tasks will ignore input and produces a single output.
%% This differs from the previous examples where each target could be evaluated on
%% various input.
